%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Homayoun}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Moradi}}}}} % Last name

	\vspace{6pt}
	
	{\large Machine Learning and \\Computer Vision Researcher} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Tehran, Poonak}\\
	\icon{Phone}{12}{+98 937 862 9071}\\
	\icon{At}{12}{\href{mailto:homoradi@ut.ac.ir}{homoradi@ut.ac.ir}}\\	
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Github}{12}{\href{https://github.com/ffletcherr}{github.com/ffletcherr}}\\
	\icon{Skype}{12}{homayouneemoradi}\\
	\icon{Google}{12}{\href{mailto:homayouneemoradi@gmail.com}{homayouneemoradi}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
		Experienced Head of R\&D  with a demonstrated history of working in Machine Learning and Computer Vision fields. Skilled AI Researcher with a Master of Science from University of Tehran.  % Dummy text

\begin{center}
	\bubbles{6/Pytorch, 4/JavaScript, 5/Opencv, 4/Pandas, 3/MongoDB}
\end{center}

\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{Computer Vision}{100}
		\baritem{Deep Learning}{80}
		\baritem{Machine Learning}{70}
		\baritem{Reinforcement Learning}{65}
		\baritem{Data Analysis}{55}
		\baritem{Robotics}{60}
		\baritem{NLP}{65}
	\end{barchart}
\end{minipage}



%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{2021 -- Presnet}
		{AI Developer}
		{Odyssey Startup Studio}
		{Develope AI-based Products Which Are Used by Canadian Startups.}
	\entry
		{2020 -- 2022\\\footnotesize{part time}}
		{Senior AI Developer}
		{ISAA Project}
		{Smart Smile Design Based-on Computer Vision Techniques.}

	\entry
		{2019 -- 2021\\\footnotesize{part time}}
		{Computer Vision Scientist}
		{SUSLIB}
		{Knowledge Extraction and Intention Recognition Using Cutting Edge AI Technologies.}

	\entry
		{2018 -- 2020\\\footnotesize{part time}}
		{Head of Computer Vision Team}
		{Control and AI Lab - IUST}
		{Multi-Agent and Autonomous Vehicles 3D Perception, Road Scene Understanding and Analysis of Surveillance Videos.}

	\entry
		{2016 -- 2018}
		{Co-Founder}
		{3DFAST}
		{The First Online 3D Printing Service and Social Marketplace Based in Tehran. We Made an Online Platform That Provides 3D Printing Services by Connecting Customers and Vendors.}
	\entry
		{2015 -- 2016}
		{Control Engineer}
		{CETEC}
		{ }		
		
\end{entrylist}


%----------------------------------------------------------------------------------------
%	PROJECT
%----------------------------------------------------------------------------------------

\cvsect{Projects}
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{2021}
	
	COVID-19 Persian Tweets Analysis
	\\Persian OCR
	\\Table Structure Recognition
	\\Face Spoofing Detection
	\\Music Metadata and Text Analysis
	
\end{minipage}
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{2020}
	
	tsetmc + Sahamyab Data Analysis
	\\Face Detection and Recognition
	\\Human Action Recognition
	\\Image Retrieval
	\\Scene Multi-Label Classification
	
\end{minipage}
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{2019}
	
	Fusion-based 3D Object Analysis
	\\Aerial Image Segmentation
	\\Supermarket Product Counter
	\\Multi Object Tracking
	
\end{minipage}	




%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2019 -- Presnet}
		{Master of Science - MS, Artificial Intelligence GPA:19.23}
		{University of Tehran}
		{Advisor: Prof. Behzad Moshiri and Dr. Mehdi Tale Masoole
		\\Thesis: Human-Robot Interaction Using Soft/Hard Information Fusion, Case Study: NAO Robot
		\\Activities: 
		\\-Research Assistant at NBIC, Supervised by Dr. MohammadReza A. Dehaqani, Human Action Classification Using EEG Signal Processing
		\\-Teaching Assistant for Big Data, Dr. Masoud Asadpour - Spring 2021
		\\ -Teaching Assistant for Information Theory and Learning, Dr. Pooya Shariatpanah, Dr. Maryam
Sabaghian - Fall 2021
		}
	\entry
		{2016 -- 2019}
		{Master of Business Administration - MBA, Finance}
		{Kharazmi University}	
		{}
	\entry
		{2012 -- 2016}
		{Bachelor's Degree, Control Engineering}
		{Iran University of Science and Technology (IUST)}
		{Advisor: Prof. Aliakbar Jalali
		\\Thesis: IoT for Smart Cities: Use Cases and Implementation Strategies
		\\Activities: Teaching Assistant for Signal and Systems, Prof. Aliakbar Jalali - Fall 2019}
	
\end{entrylist}


%----------------------------------------------------------------------------------------
%	Papers
%----------------------------------------------------------------------------------------


\cvsect{Papers}

\begin{entrylist}
	\entry
		{ICRoM 2021}
		{Robots Learn Visual Pouring Task Using Deep Reinforcement Learning with Minimal Human
Effort}
		{H.Moradi, M.T.Masouleh, B.Moshiri}	
		{The entire pipeline for teaching a robot to perform the visual pouring task is addressed with a
minimal human supervision. The reinforcement learning approach is employed without the use
of reward engineering where the reward function is approximated by a Convolutional Neural Net-
work.}
\end{entrylist}



%----------------------------------------------------------------------------------------
%	HONORS
%----------------------------------------------------------------------------------------



\cvsect{HONORS}
\renewcommand\labelitemi{\large$\bullet$}
\begin{itemize}

\item First Rank in DataDays2021 Challenge. Design a Recommender System Based-on Hybrid Approach for torob.com

\item 5th Rank in DigiCup2021 (Data Science).

\item 33th Rank in the Iranian University Entrance Exam for master’s degree in Artificial Intelligence.
\end{itemize}


%----------------------------------------------------------------------------------------
%	Other Tech Skills
%----------------------------------------------------------------------------------------



\cvsect{Other Tech Skills}
\renewcommand\labelitemi{\large$\bullet$}
\begin{itemize}

\item Familiar with SQL and Redis.

\item Robotics Operating System (ROS).

\item 3Build and Deploy Machine Learning Web Apps Using JavaScript.

\item Working with Deep Learning Optimization Tools (TensorRT, ONNX)

\item Build AI Services Using Docker and ML Serving Tools Like Torch-Serve, Triton, Ray.

\item Familiar with Generative Networks, Transformers, and Audio Processing Techniques.

\item Familiar with Useful AI Frameworks like HuggingFace, stable-baselines3, RLlib, MMlab, Gensim, Spacy, Kornia, JAX, ... .

\end{itemize}


%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------


\cvsect{REFERENCES}

\begin{entrylist}
	\entry
		{ }
		{Prof. Behzad Moshiri {\small(moshiri@ut.ac.ir)}}
		{Professor in University of Tehran}	
		{My Master’s Thesis Supervisor.}
	\entry
		{ }
		{Dr. Mehdi Tale Masouleh {\small(m.t.masouleh@ut.ac.ir)}}
		{Associate Professor in University of Tehran}	
		{My Master’s Thesis Supervisor.}		
	\entry
		{ }
		{Dr. Mohammad Hossein Rohban {\small(rohban@sharif.edu)}}
		{Assistant Professor in Sharif University}	
		{Scientific Supervision in ISAA Project.}
	\entry
		{ }
		{Dr. Saeed Shamaghdari {\small(shamaghdari@iust.ac.ir)}}
		{Associate Professor in IUST}	
		{Supervisor of Control and AI lab inIran University of Science and Technology (IUST).}
	\entry
		{ }
		{Amir Houieh {\small(amir@suslib.com)}}
		{Co-Founder of SUSLIB}	
		{ }

		
\end{entrylist}


\end{document}
